Higher-Order unification for free!

### 2024-04-12 paper/main.tex
if only I was a native speaker...

  In this paper we propose a better-behaved encoding \Ho,
  and show how to map unification problems in \Fo{}
  to related problems in \Ho.
    As a result we can lift the ML
  higher-order unification procedure to \Fo{} in a way that it
  honours $\eta\beta$-equivalence (for CIC functions), solves
  problems in the pattern fragment and finally allows
  for the addition of heuristics to deal with problems outside the
  pattern fragment. The unification procedure we build can be used to
  efficiently simulate a logic program in \Fo{} by re-using optimizations
  provided by the ML such as clause indexing.

>>>>

  In this paper we propose a better-behaved encoding \Ho,
  and show how to map unification problems in \Fo{}
  to related problems in \Ho.
    As a result we obtain \Uo{}, a higher-order unification procedure for \Fo{}
    that honours $\eta\beta$-equivalence (for CIC functions), solves
  problems in the pattern fragment and allows
  for the use of heuristics to deal with problems outside the
  pattern fragment. Moreover, since \Uo{} delegates most of the work to \Ue,
  it can be used to efficiently simulate a logic program in \Fo{} by
  taking advantage of
  unification-related optimizations of the ML, such as clause indexing.
